Dialect: A Compact Line Notation Based on SMILES

### 2022-06-19 manuscript.tex
Adds figure for reprepsentative dialect examples. closes #114
Adds figure tree vs. graph. closes #115

@@

\begin{figure}
\centering
\includegraphics{filler}
\caption{Representative Dialect examples.}
\label{fig:myfig}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Tree vs. Graph.}
    \label{fig:tree-vs-graph}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{representative-examples.pdf}
\caption{Representative Dialect examples.}
\label{fig:myfig}
\end{figure}

@@

@@

\begin{figure}
    \centering
    \includegraphics[width=6cm]{molecular-graph-vs-tree.pdf}
    \caption{Molecular Graph vs. Molecular Tree. The bonds in a molecular graph reference atoms indirectly through unique indexes (lower left). In contrast, a bond in a molecular tree defines its target atom inline (lower right). This increases the potential efficiency of trees over graphs for molecular representation. To simulate ring closure, a molecular tree introduces bridge nodes, as described later (solid grey circles).}
    \label{fig:molecular-graph-vs-tree}
\end{figure}
